
# Reading the data from CSV file and storing it in a variable
```{r}
dataset <- read.csv("C:/Users/user/Desktop/Task1.csv")
```

# Plotting the data to check if hours & scores are linearly related
```{r}
plot(dataset$Hours,dataset$Scores,xlab = "Hours Studied",ylab = "Percentage Score",
     main = "Hours vs Percentage")
```

# Since the scatterplot is linear, we can use linear regression to predict the scores

# Splitting the data into training set and test set
```{r}
library(caTools)
set.seed(123)
split = sample.split(dataset$Scores, SplitRatio = 0.8)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)
```

# Fitting simple linear regression to the training set
```{r}
regressor = lm(formula = Scores ~ Hours, data = training_set)
```

# Predicting the test results
```{r}
y_pred = predict(regressor, newdata = test_set)
```

# Visualizing the Training set results

```{r}
library(ggplot2)
ggplot() + 
  geom_point(aes(x = training_set$Hours, y = training_set$Scores),
                 colour = 'Red') +
  geom_line(aes(x= training_set$Hours, y = predict(regressor, newdata = training_set)),
            colour = 'Blue') +
  ggtitle('Scores vs Hours (Training Set)') +
  xlab('Hours Studied') +
  ylab('Percentage Score')
```

# Visualizing the Test set results
```{r}
ggplot() +
  geom_point(aes(x = test_set$Hours, y = test_set$Scores),
             colour = 'Red') +
  geom_line(aes(x = training_set$Hours, y = predict(regressor, newdata = training_set)),
            colour = 'Blue') +
  ggtitle('Scores vs Hours (test Set)') +
  xlab('Hours Studied') +
  ylab('Percentage Scores')
```

# Predicting the score for studying 9.25 hrs a day (Question)
```{r}
newset <- data.frame("Hours" = 9.25, "Scores" = 0)
own_score_prediction <- predict(regressor, newdata = newset)
newset <- data.frame("Hours" = 9.25, "Scores" = own_score_prediction)
print(newset)
```

#Plotting the Predicted result against the regression line
```{r}
ggplot() + 
  geom_point(aes(x = training_set$Hours, y = training_set$Scores),
             colour = 'Black') +
  geom_point(aes(x = test_set$Hours, y = test_set$Scores),
             colour = 'Green') +
  geom_point(aes(x = newset$Hours, y = newset$Scores),
             colour = 'Red', size = 7) +
  geom_line(aes(x= training_set$Hours, y = predict(regressor, newdata = training_set)),
            colour = 'Blue') +
  ggtitle('Scores vs Hours (Test Set)') +
  xlab('Hours Studied') +
  ylab('Percentage Score')
```
